---
params:
  GeneList: !r c("PENK","APOE","SSSDDF","DRD1")
  NAME: Annotation
  VERBOSE: no
---
<!--   -->
<!-- Rmarkdown skeleton type -->
<!-- depends on: -->
<!-- -R librairies -->
<!-- --rmarkdown -->
<!-- --DT will be used for their data table -->
<!-- -Other Ressources -->
<!-- --/bioinfo/users/ltaing/DATA_TMP/ltaing/PrettyAnnotInR/Annot.R -->
<!-- ---Absolute path of a R file -->
<!-- ---R Script that will create at the same location of the WD a ressource directory if need be of some ressources to be computed -->
<!-- Parameters -->
<!-- GeneList: the list of gene to annotate -->
<!--   Vector of official gene symbol -->
<!--   -can contained duplicated entries. -->
<!--   -will discard duplicated -->
<!-- NAME: The title of the H1 html chunck -->
<!--   Scalar of the title -->
<!--   -character -->
<!-- VERBOSE: boolean for outputing or not the R session and the passed parameters -->
<!-- Usage: -->
<!-- in a R session case a) -->

<!-- library("rmarkdown") -->
<!-- render(input="AnnotationSktln.Rmd", -->
<!--       output_format="html_document", -->
<!--       output_file="MyOutputfile.html", -->
<!--       params=list( -->
<!--         GeneList=ListOfGenesToAnnotate, #Vector of Official Gene Symbol as used in org.Hs.eg.db -->
<!--         VERBOSE=FALSE, # Boolean -->
<!--         NAME="The name of the chunk" # scalar of a string that will be use as title for the chunk -->
<!--       )) -->

<!-- in a Rmd case b)  -->
<!-- the params list must be initialized before calling the .Rmd as a child -->

<!-- ```{r} -->
<!-- I<-read.table("annotation.txt",header=TRUE,sep="\t",quote="\"") -->
<!-- params <- list(GeneList = as.vector(I$GENE), -->
<!--                VERBOSE=FALSE, NAME="Patrick's list") -->
<!-- ``` -->
<!-- ```{r child="AnnotationSkltn.Rmd"} -->
<!-- ``` -->

<!-- ```{r JustMyImagination} -->
<!-- params <- list(GeneList = c("PENK","DRD1","DRD2","APOE"), -->
<!--                VERBOSE=FALSE, NAME="Memories of day's gone") -->
<!-- ``` -->
<!-- ```{r child="AnnotationSkltn.Rmd"} -->
<!-- ``` -->
<!-- ---> 

```{r include=FALSE}
knitr::opts_chunk$set(echo = params$VERBOSE,
                      warning=params$VERBOSE,
                      fig.width = 7,
                      fig.align="center")
library("DT")
source("/bioinfo/users/ltaing/DATA_TMP/ltaing/PrettyAnnotInR/Annot.R")
MyGeneList<-unique(params$GeneList)
```

```{r results='asis',echo=FALSE}
cat("# ",params$NAME," {.tabset}\n\n",sep="")
```
## Description {.tabset}

### Resume

Gene list composed of `r length(params$GeneList)` entries.
Among them `r sum(MyGeneList %in% BP2Genes$Gene_Symbol)` (`r round( sum( MyGeneList %in% BP2Genes$Gene_Symbol )/length( MyGeneList ), 2 )*100`%) have an entry in Homo Sapiens gene ontology biological process database.

Among them `r sum(MyGeneList %in% CC2Genes$Gene_Symbol)` (`r round( sum( MyGeneList %in% CC2Genes$Gene_Symbol )/length( MyGeneList ), 2 )*100`%) have an entry in Homo Sapiens gene ontology cellular component database.

Among them `r sum(MyGeneList %in% MF2Genes$Gene_Symbol)` (`r round( sum( MyGeneList %in% MF2Genes$Gene_Symbol )/length( MyGeneList ), 2 )*100`%) have an entry in Homo Sapiens gene ontology molecular function database.

Among them `r sum(MyGeneList %in% Kegg2Genes$Gene_Symbol)` (`r round( sum( MyGeneList %in% Kegg2Genes$Gene_Symbol )/length( MyGeneList ), 2 )*100`%) have an entry in Homo Sapiens KEGG database.

Among them `r sum(MyGeneList %in% R2Genes$Gene_Symbol)` (`r round( sum( MyGeneList %in% R2Genes$Gene_Symbol )/length( MyGeneList ), 2 )*100`%) have an entry in Homo Sapiens reactome database.

Among them `r sum(MyGeneList %in% P2Genes$Gene_Symbol)` (`r round( sum( MyGeneList %in% P2Genes$Gene_Symbol )/length( MyGeneList ), 2 )*100`%) have an entry in Homo Sapiens panther database.

### Detail

```{r echo=FALSE}
#Create a matrix for each gene symbol to know if it is present inside each ressource database
#and some summary description
Matrix <- matrix(0, ncol = 6, nrow = length(MyGeneList))
rownames(Matrix) <- MyGeneList
colnames(Matrix) <- c("BP", "MF", "CC", "KEGG", "Panther", "reactome")
Matrix[MyGeneList %in% BP2Genes$Gene_Symbol, "BP"] <- 1
Matrix[MyGeneList %in% CC2Genes$Gene_Symbol, "CC"] <- 1
Matrix[MyGeneList %in% MF2Genes$Gene_Symbol, "MF"] <- 1
Matrix[MyGeneList %in% Kegg2Genes$Gene_Symbol, "KEGG"] <- 1
Matrix[MyGeneList %in% P2Genes$Gene_Symbol, "Panther"] <- 1
Matrix[MyGeneList %in% R2Genes$Gene_Symbol, "reactome"] <- 1
Matrix[Matrix == 0] <- "absent"
Matrix[Matrix == 1] <- "present"
DF <- data.frame(Matrix)
DF$Gene <- rownames(DF)
#Some kind of sql select to use the org.Hs.eg.db
DF$Description <- mapIds(
  org.Hs.eg.db,
  keys = as.vector(DF$Gene),
  keytype = "SYMBOL",
  column = "GENENAME"
)
DF <- DF[, c("Gene",
             "Description",
             "BP",
             "MF",
             "CC",
             "KEGG",
             "Panther",
             "reactome")]
#Pretty output using java script
DT::datatable(
  DF,
  rownames = FALSE,
  filter = 'top',
  options = list(autoWidth = TRUE)
)

```

## Biological process

```{r echo=FALSE}
#Biological process results from the annot.R script
ResultsBP<-OneTestGoKeggPanther(GeneList=MyGeneList,
                              Ressource = "BP",
                              pretty=TRUE)
#datatable(ResultsBP,rownames=FALSE,extensions = "Buttons",
#          options=list(dom='Bfrtip',buttons=I('colvis')))

DT::datatable(ResultsBP, #the dataframe to be output
          rownames=FALSE, # hidding the rownames
          extensions = 'Responsive', # allowing the hidding of certain columns
          options=list(columnDefs=list(list(className="none",targets=8) #hidding the eight column
                                  )
                      )
)


#datatable(ResultsBP, extensions = 'Responsive')
```

## Molecular function

```{r echo=FALSE}
ResultsMF<-OneTestGoKeggPanther(GeneList=MyGeneList,
                              Ressource = "MF",
                              pretty=TRUE)
datatable(ResultsMF,
          rownames=FALSE,
          extensions = 'Responsive',
          options=list(columnDefs=list(list(className="none",targets=8)
                                  )
                      )
)
```

## Celular component

```{r echo=FALSE}
ResultsCC<-OneTestGoKeggPanther(GeneList=MyGeneList,
                              Ressource = "CC",
                              pretty=TRUE)
datatable(ResultsCC,
          rownames=FALSE,
          extensions = 'Responsive',
          options=list(columnDefs=list(list(className="none",targets=8)
                                  )
                      )
)
```

## Kegg

```{r echo=FALSE}
ResultsKegg<-OneTestGoKeggPanther(GeneList=MyGeneList,
                              Ressource = "KEGG",
                              pretty=TRUE)
datatable(ResultsKegg,
          rownames=FALSE,
          extensions = 'Responsive',
          options=list(columnDefs=list(list(className="none",targets=8)
                                  )
                      )
)
```

## Panther

```{r echo=FALSE}
ResultsPnthr<-OneTestGoKeggPanther(GeneList=MyGeneList,
                              Ressource = "Panther",
                              pretty=TRUE)
datatable(ResultsPnthr,
          rownames=FALSE,
          extensions = 'Responsive',
          options=list(columnDefs=list(list(className="none",targets=8)
                                  )
                      )
)
```

## Reactome

```{r echo=FALSE}
ResultsRctm<-OneTestGoKeggPanther(GeneList=MyGeneList,
                              Ressource = "reactome",
                              pretty=TRUE)
datatable(ResultsRctm,
          rownames=FALSE,
          extensions = 'Responsive',
          options=list(columnDefs=list(list(className="none",targets=8)
                                  )
                      )
)
```

<!-- if the verbose boolean is set to true then compute the next chunks -->
<!-- in this case it will output some supplementary informations for the  -->

```{r eval=params$VERBOSE,results="asis"}
cat("# Infos {.tabset}

## Parameters
")
```

```{r eval=params$VERBOSE}
PARAMETERS<-unlist(params)
PARAMETERS.DF<-data.frame(PARAMETER=names(PARAMETERS),VALUE=PARAMETERS)
datatable(PARAMETERS.DF,row.names = FALSE)
```

```{r eval=params$VERBOSE,results="asis"}
cat("## Session
")
```
```{r eval=params$VERBOSE}
sessionInfo()
```


